The hydra and the rooster

### 2020-07-23 latex/chapter-schutte.tex
redaction introduction to ordinals

\label{chap:schutte}

@@

Let us declare a type 
\texttt{ON} for representing countable ordinals, and a binary relation
 \texttt{lt}. Note that, in our development, \texttt{ON} is a type, while the \emph{set} of countable ordinals (called $\mathbb{O}$ by Schütte) 
is the full set over the type \texttt{ON}.

\index{Types!ON@ON (countable ordinals)}

@@

\begin{Coqsrc}
Parameter ON : Type.
Parameter lt : relation ON.
Notation "a < b" := (lt a b): schutte_scope.

Definition ordinal := Full_set ON.
\end{Coqsrc}

@@

\begin{Coqsrc}
Axiom AX2 : forall X: Ensemble ON, 
   (exists a,  (forall y, In X y -> y < a)) ->
   countable X.

Axiom AX3 : forall X : Ensemble ON,
              countable X -> 
              exists a,  forall y, In X y -> y < a.
\end{Coqsrc}

@@

According to the  definition of a well order, every non-empty subset of \texttt{ON} has a least element. Furthermore, this least element is unique.

\begin{Coqsrc}
Remark R : exists! z : ON, least_member lt  ordinal z.
Proof.
  destruct inh_ON as [a]; apply (well_order (WO:=AX1)) with a .
  split.
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition zero : ON.
Proof.
  Fail destruct R.
\end{Coqsrc}

@@

In order to use these tools,  we had to tell \coq{}  that the type \texttt{ON} is not empty:

\begin{Coqsrc}
Axiom inh_ON : inhabited ON.
\end{Coqsrc}

@@

\index{Constants!zero:ON}

\begin{Coqsrc}
Definition zero: ON :=the_least ordinal.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma zero_le (alpha : ON) :  zero <= alpha.
Proof.
  unfold zero, the_least, the; apply iota_ind.
\end{Coqsrc}

According to the use of the description operator \texttt{iota}, we have to solve  two trivial sub-goals.
\begin{enumerate}
\item Prove that there exists a unique least member of \texttt{ON}
\item Prove that being a least member of \texttt{ON} entails the announced inequality 
\end{enumerate}

@@

  alpha : ON
  ============================
  exists ! x : ON, least_member lt ordinal x

subgoal 2 (ID 156) is:
 forall a : ON, unique (least_member lt ordinal) a -> 
                a <= alpha
\end{Coqanswer}

@@

 Definition bottom := the_least (Empty_set ON).
\end{Coqbad}

@@

Since we won't be able to prove the proposition
\linebreak \Verb|{exists! a: ON, least_member (Empty_set ON) a|, the only properties we would be able to prove about \texttt{bottom} would be \emph{trivial} properties, 
\emph{i.e.}, satisfied by \emph{any} element of type \texttt{ON}, like for instance
\texttt{bottom = bottom}, or \texttt{zero <= bottom}.

@@

  ============================
  exists ! x : ON, least_member lt (Empty_set ON) x

subgoal 2 (ID 414) is:
 forall a : ON, unique (least_member lt (Empty_set ON)) a -> 
      a <= zero
\end{Coqanswer}

@@

The definition of the function \texttt{succ:ON -> ON} is very concise. The successor of any ordinal $\alpha$ is the smallest ordinal strictly greater than $\alpha$.

\index{Functions!succ (in type ON)}

\begin{Coqsrc}
Definition succ (alpha : ON) := the_least (fun beta => alpha < beta).
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition is_succ (alpha:ON) := exists beta, alpha = succ beta.

Definition is_limit (alpha:ON) := alpha <> zero /\ ~ is_succ alpha.
\end{Coqsrc}

@@

Fixpoint finite (i:nat) : ON :=
  match i with 
            | 0 => zero
            | S i => succ (F i)
  end
where "'F' i" := (finite i)  : schutte_scope.

Coercion finite : nat >-> ON.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition succ_spec (alpha:ON) :=
  least_member   lt (fun z => alpha < z).
\end{Coqsrc}

@@

  alpha : ON
  ============================
  exists ! x : ON, succ_spec alpha x
\end{Coqanswer}

@@

\begin{Coqsrc}
Lemma lt_succ (alpha : ON) :  alpha < succ alpha.
Proof.
  destruct  (succ_ok  alpha);  tauto.
Qed.

@@

Lemma lt_succ_le (alpha beta : ON):
  alpha < beta -> succ alpha <= beta.
Proof with eauto with schutte.
  intros  H;  pattern (succ alpha); apply the_least_ok ... 
  exists (succ alpha); red;apply lt_succ ...
Qed.
\end{Coqsrc}

\begin{Coqsrc}
Lemma lt_succ_le_2 (alpha beta : ON):
  alpha < succ beta -> alpha <= beta.

Lemma succ_mono (alpha beta : ON):
  alpha < beta -> succ alpha < succ beta.

Lemma succ_monoR (alpha beta : ON) :
 succ alpha < succ beta -> alpha < beta.

Lemma lt_succ_lt (alpha beta : ON) :
  is_limit beta ->  alpha < beta -> succ alpha < beta.
\end{Coqsrc}

@@

Definition sup (X: Ensemble ON) : ON  := the  (sup_spec X).

@@

Then, we define the function \texttt{omega\_limit} which returns the least upper bound 
of the  (denumerable) range of any sequence \texttt{s: nat -> ON}. 
By \texttt{AX3} this range is bounded, hence the set of its upper bounds is not empty and has a least element.

\begin{Coqsrc}
Definition omega_limit (s:nat->ON) : ON 
  := |_| (seq_range s).
\end{Coqsrc}

@@

Lemma lt_omega_finite alpha : ON) : 
  alpha < omega ->  exists i:nat, alpha =  i.

@@

\begin{Coqsrc}
 Definition segment (A: Ensemble ON) :=
  forall alpha beta, In A alpha -> beta < alpha -> In A  beta.

Definition proper_segment (A: Ensemble ON) :=
  segment A /\ ~ Same_set A ordinal.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition ordering_function (f : ON -> ON)(A B : Ensemble ON) :=
 segment A /\
 (forall a, In A a -> In B (f a)) /\
 (forall b, B b -> exists a, In A a /\ f a = b) /\
 forall a b, In A a -> In A b -> a < b ->  f a < f b.

Definition ordering_segment (A B : Ensemble ON) :=
  exists f : ON -> ON, ordering_function f A B.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition the_ordering_segment (B : Ensemble ON) :=
  the  (fun x => ordering_segment x B).

Definition ord  (B : Ensemble ON) := 
  some (fun f => ordering_function f (the_ordering_segment B) B).
\end{Coqsrc}

@@

\begin{Coqanswer}
forall B : Ensemble ON,
 exists ! S : Ensemble ON, 
      exists f : ON -> ON, ordering_function f S B
\end{Coqanswer}

\begin{Coqanswer}
ordering_function_unicity :
forall (B S1 S2 : Ensemble ON) (f1 f2 : ON -> ON),
ordering_function f1 S B ->
ordering_function f2 S2 B -> 
fun_equiv f1 f2 S1 S2
\end{Coqanswer}

@@

Th_13_5_2 :
forall (A B : Ensemble ON) (f : ON -> ON),
ordering_function f A B -> Closed B -> continuous f A B
\end{Coqsrc}

@@

We are now ready to define and study addition on the type \texttt{ON}.
The following definitions and proofs can be consulted in Module
\href{../src/html/hydras.Schutte.Addition.html}%
{\texttt{Schutte.Addition.v}}.

@@

\begin{Coqsrc}
Lemma plus_elim (alpha : ON) :
  forall P : (ON->ON)->Prop,
    (forall f: ON->ON, 
        ordering_function f ordinal (ge alpha)-> P f) ->
    P (plus alpha).
\end{Coqsrc}

\begin{Coqsrc}
Lemma alpha_plus_zero (alpha: ON): alpha + zero = alpha.
Proof.
 pattern  (plus alpha); apply plus_elim; eauto.
 \end{Coqsrc}

@@

  alpha : ON
  ============================
  forall f : ON -> ON,
  ordering_function f ordinal (ge alpha) -> 
  f zero = alpha
 \end{Coqanswer}

@@

Lemma zero_plus_alpha (alpha : ON) : zero + alpha = alpha.

Lemma le_plus_l (alpha beta : ON) : alpha <= alpha + beta.

Lemma le_plus_r (alpha beta : ON) :  beta <= alpha + beta.

Lemma plus_mono_r (alpha beta gamma : ON) : 
    beta < gamma -> alpha + beta < alpha + gamma.

Lemma plus_of_succ (alpha beta : ON) :
    alpha + (succ beta) = succ (alpha + beta).

Theorem plus_assoc (alpha beta gamma : ON) :
  alpha + (beta + gamma) = (alpha + beta) + gamma.

@@

Lemma finite_plus_ge_omega (n : nat) (alpha : ON) :
  omega <= alpha -> n + alpha = alpha.
\end{Coqsrc}

@@

\begin{Coqsrc}
Fixpoint mult_Sn (alpha:ON)(n:nat){struct n} :ON :=
 match n with 
            | 0 => alpha
            | S p => mult_Sn alpha p + alpha
 end.

@@

\begin{Coqsrc}
Definition AP : Ensemble ON :=
  fun alpha => 
  zero < alpha /\
  (forall beta, beta < alpha ->  beta + alpha = alpha).
\end{Coqsrc}

@@

\begin{Coqsrc}
Fixpoint omega_tower (i : nat) : ON :=
  match i with
    0 =>  1
  | S j => phi0 (omega_tower j)
  end.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma AP_plus_closed (alpha beta gamma : ON): 
     In AP alpha -> beta < alpha -> gamma < alpha -> beta + gamma < alpha.

@@

\begin{Coqsrc} 
Definition Closed (B : Ensemble ON) : Prop := 
  forall M, Included M B -> Inhabited _ M -> 
                 countable M -> In B (|_| M).
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma AP_phi0 (alpha : ON) : In AP (phi0 alpha).

@@

Lemma phi0_mono (alpha beta : ON) :
  alpha < beta ->  phi0 alpha < phi0 beta.

Lemma phi0_inj (alpha beta : ON) :
    phi0 alpha = phi0 beta -> alpha = beta.

Lemma phi0_sup : forall (U: Ensemble ON),
   Inhabited _ U ->   countable U ->  phi0 (|_| U) = |_| (image U phi0).

Lemma is_limit_phi0 (alpha : ON) :
  zero < alpha ->  is_limit (phi0 alpha).

@@

Lemma phi0_le (alpha : ON) : alpha <= phi0 alpha.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma lt_phi0 (alpha : ON):
  alpha < epsilon0 -> alpha < phi0 alpha.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition Cr_fun : forall alpha : ON,
       (forall beta : ON, beta < alpha -> Ensemble ON) ->
        Ensemble ON 
:= 
   fun (alpha :ON)
        (Cr : forall beta, 
                beta < alpha -> Ensemble ON) 
        (x : ON) => (
       (alpha = zero /\ AP x) \/
       (zero < alpha /\
        forall beta (H:beta < alpha),
          the_ordering_segment (Cr beta H) x /\ ord (Cr  beta H) x = x)).

Definition Cr (alpha : ON) : Ensemble ON := 
    (Fix  all_ord_acc (fun (_:ON) => Ensemble ON) Cr_fun) alpha.
\end{Coqsrc}

\begin{Coqsrc}
Definition phi (alpha : ON) : ON -> ON 
    :=  ord (Cr alpha).

Definition A (alpha : ON) : Ensemble ON :=
  the_ordering_segment (Cr alpha).
\end{Coqsrc}

@@

\begin{Coqsrc}
Section Proof_of_Lemma5.
  Let P (alpha:ON) := Unbounded (Cr alpha) /\ Closed (Cr alpha).

@@

\begin{Coqsrc}
 Definition cnf_t := list ON.

Fixpoint eval (l : cnf_t) : ON :=
  match l with nil => zero
              | beta :: l' => phi0 beta + eval l'
  end.

@@

Definition is_cnf_of (alpha : ON)(l : cnf_t) : Prop :=
  sorted l /\ alpha = eval l.
\end{Coqsrc}

@@

\begin{Coqsrc}
Theorem cnf_exists (alpha : ON) :
  exists l: cnf_t, is_cnf_of alpha l.
\end{Coqsrc}

@@

Theorem cnf_exists_unique (alpha:ON) :
  exists! l: cnf_t, is_cnf_of alpha l.
\end{Coqsrc}

@@

\section{An embedding of \texttt{T1} into \texttt{ON}}

Our library 
\href{../src/html/hydras.Schutte.Injection_from_T1.html}%
{\texttt{Schutte.Injection\_from\_T1.v}} establishes the link between two very different modelizations of ordinal numbers. In other words, it ``validates'' a data structure in terms of
a classical mathematical discourse considered as a model. 
First, we define a function from \texttt{T1} into  \texttt{ON} by structural recursion.

\begin{Coqsrc}
Fixpoint inject (t:T1) : ON :=
 match t with 
     | T1.zero => zero
     | T1.ocons a n b =>  AP.phi0 (inject a) * S n + inject b
 end.  
\end{Coqsrc}

@@

Finally, we prove that \texttt{inject} is a bijection from the set of all terms of \texttt{T1} in normal form to the set 
\texttt{members epsilon0} of the elements of \texttt{ON} strictly less than  $\epsilon_0$.

>>>>

\label{chap:schutte} 
%ON

@@

Let us declare a type 
\texttt{Ord} for representing countable ordinals, and a binary relation
 \texttt{lt}. Note that, in our development, \texttt{Ord} is a type, while the \emph{set} of countable ordinals (called $\mathbb{O}$ by Schütte) 
is the full set over the type \texttt{Ord}.

\index{Types!Ord@Ord (countable ordinals)}

@@

\begin{Coqsrc}
Parameter Ord : Type.
Parameter lt : relation Ord.
Notation "a < b" := (lt a b): schutte_scope.

Definition ordinal := Full_set Ord.
\end{Coqsrc}

@@

\begin{Coqsrc}
Axiom AX2 : forall X: Ensemble Ord, 
   (exists a,  (forall y, In X y -> y < a)) ->
   countable X.

Axiom AX3 : forall X : Ensemble Ord,
              countable X -> 
              exists a,  forall y, In X y -> y < a.
\end{Coqsrc}

@@

According to the  definition of a well order, every non-empty subset of \texttt{Ord} has a least element. Furthermore, this least element is unique.

\begin{Coqsrc}
Remark R : exists! z : Ord, least_member lt  ordinal z.
Proof.
  destruct inh_Ord as [a]; apply (well_order (WO:=AX1)) with a .
  split.
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition zero : Ord.
Proof.
  Fail destruct R.
\end{Coqsrc}

@@

In order to use these tools,  we had to tell \coq{}  that the type \texttt{Ord} is not empty:

\begin{Coqsrc}
Axiom inh_Ord : inhabited Ord.
\end{Coqsrc}

@@

\index{Constants!zero:Ord}

\begin{Coqsrc}
Definition zero: Ord :=the_least ordinal.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma zero_le (alpha : Ord) :  zero <= alpha.
Proof.
  unfold zero, the_least, the; apply iota_ind.
\end{Coqsrc}

According to the use of the description operator \texttt{iota}, we have to solve  two trivial sub-goals.
\begin{enumerate}
\item Prove that there exists a unique least member of \texttt{Ord}
\item Prove that being a least member of \texttt{Ord} entails the announced inequality 
\end{enumerate}

@@

  alpha : Ord
  ============================
  exists ! x : Ord, least_member lt ordinal x

subgoal 2 (ID 156) is:
 forall a : Ord, unique (least_member lt ordinal) a -> 
                a <= alpha
\end{Coqanswer}

@@

 Definition bottom := the_least (Empty_set Ord).
\end{Coqbad}

@@

Since we won't be able to prove the proposition
\linebreak \Verb|{exists! a: Ord, least_member (Empty_set Ord) a|, the only properties we would be able to prove about \texttt{bottom} would be \emph{trivial} properties, 
\emph{i.e.}, satisfied by \emph{any} element of type \texttt{Ord}, like for instance
\texttt{bottom = bottom}, or \texttt{zero <= bottom}.

@@

  ============================
  exists ! x : Ord, least_member lt (Empty_set Ord) x

subgoal 2 (ID 414) is:
 forall a : Ord, unique (least_member lt (Empty_set Ord)) a -> 
      a <= zero
\end{Coqanswer}

@@

The definition of the function \texttt{succ:Ord -> Ord} is very concise. The successor of any ordinal $\alpha$ is the smallest ordinal strictly greater than $\alpha$.

\index{Functions!succ (in type Ord)}

\begin{Coqsrc}
Definition succ (alpha : Ord) := the_least (fun beta => alpha < beta).
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition is_succ (alpha:Ord) := exists beta, alpha = succ beta.

Definition is_limit (alpha:Ord) := alpha <> zero /\ ~ is_succ alpha.
\end{Coqsrc}

@@

Fixpoint finite (i:nat) : Ord :=
  match i with 
            | 0 => zero
            | S i => succ (F i)
  end
where "'F' i" := (finite i)  : schutte_scope.

Coercion finite : nat >-> Ord.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition succ_spec (alpha:Ord) :=
  least_member   lt (fun z => alpha < z).
\end{Coqsrc}

@@

  alpha : Ord
  ============================
  exists ! x : Ord, succ_spec alpha x
\end{Coqanswer}

@@

\begin{Coqsrc}
Lemma lt_succ (alpha : Ord) :  alpha < succ alpha.
Proof.
  destruct  (succ_ok  alpha);  tauto.
Qed.

@@

Lemma lt_succ_le (alpha beta : Ord):
  alpha < beta -> succ alpha <= beta.
Proof with eauto with schutte.
  intros  H;  pattern (succ alpha); apply the_least_ok ... 
  exists (succ alpha); red;apply lt_succ ...
Qed.
\end{Coqsrc}

\begin{Coqsrc}
Lemma lt_succ_le_2 (alpha beta : Ord):
  alpha < succ beta -> alpha <= beta.

Lemma succ_mono (alpha beta : Ord):
  alpha < beta -> succ alpha < succ beta.

Lemma succ_monoR (alpha beta : Ord) :
 succ alpha < succ beta -> alpha < beta.

Lemma lt_succ_lt (alpha beta : Ord) :
  is_limit beta ->  alpha < beta -> succ alpha < beta.
\end{Coqsrc}

@@

Definition sup (X: Ensemble Ord) : Ord  := the  (sup_spec X).

@@

Then, we define the function \texttt{omega\_limit} which returns the least upper bound 
of the  (denumerable) range of any sequence \texttt{s: nat -> Ord}. 
By \texttt{AX3} this range is bounded, hence the set of its upper bounds is not empty and has a least element.

\begin{Coqsrc}
Definition omega_limit (s:nat->Ord) : Ord 
  := |_| (seq_range s).
\end{Coqsrc}

@@

Lemma lt_omega_finite alpha : Ord) : 
  alpha < omega ->  exists i:nat, alpha =  i.

@@

\begin{Coqsrc}
 Definition segment (A: Ensemble Ord) :=
  forall alpha beta, In A alpha -> beta < alpha -> In A  beta.

Definition proper_segment (A: Ensemble Ord) :=
  segment A /\ ~ Same_set A ordinal.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition ordering_function (f : Ord -> Ord)(A B : Ensemble Ord) :=
 segment A /\
 (forall a, In A a -> In B (f a)) /\
 (forall b, B b -> exists a, In A a /\ f a = b) /\
 forall a b, In A a -> In A b -> a < b ->  f a < f b.

Definition ordering_segment (A B : Ensemble Ord) :=
  exists f : Ord -> Ord, ordering_function f A B.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition the_ordering_segment (B : Ensemble Ord) :=
  the  (fun x => ordering_segment x B).

Definition ord  (B : Ensemble Ord) := 
  some (fun f => ordering_function f (the_ordering_segment B) B).
\end{Coqsrc}

@@

\begin{Coqanswer}
forall B : Ensemble Ord,
 exists ! S : Ensemble Ord, 
      exists f : Ord -> Ord, ordering_function f S B
\end{Coqanswer}

\begin{Coqanswer}
ordering_function_unicity :
forall (B S1 S2 : Ensemble Ord) (f1 f2 : Ord -> Ord),
ordering_function f1 S B ->
ordering_function f2 S2 B -> 
fun_equiv f1 f2 S1 S2
\end{Coqanswer}

@@

Th_13_5_2 :
forall (A B : Ensemble Ord) (f : Ord -> Ord),
ordering_function f A B -> Closed B -> continuous f A B
\end{Coqsrc}

@@

We are now ready to define and study addition on the type \texttt{Ord}.
The following definitions and proofs can be consulted in Module
\href{../src/html/hydras.Schutte.Addition.html}%
{\texttt{Schutte.Addition.v}}.

@@

\begin{Coqsrc}
Lemma plus_elim (alpha : Ord) :
  forall P : (Ord->Ord)->Prop,
    (forall f: Ord->Ord, 
        ordering_function f ordinal (ge alpha)-> P f) ->
    P (plus alpha).
\end{Coqsrc}

\begin{Coqsrc}
Lemma alpha_plus_zero (alpha: Ord): alpha + zero = alpha.
Proof.
 pattern  (plus alpha); apply plus_elim; eauto.
 \end{Coqsrc}

@@

  alpha : Ord
  ============================
  forall f : Ord -> Ord,
  ordering_function f ordinal (ge alpha) -> 
  f zero = alpha
 \end{Coqanswer}

@@

Lemma zero_plus_alpha (alpha : Ord) : zero + alpha = alpha.

Lemma le_plus_l (alpha beta : Ord) : alpha <= alpha + beta.

Lemma le_plus_r (alpha beta : Ord) :  beta <= alpha + beta.

Lemma plus_mono_r (alpha beta gamma : Ord) : 
    beta < gamma -> alpha + beta < alpha + gamma.

Lemma plus_of_succ (alpha beta : Ord) :
    alpha + (succ beta) = succ (alpha + beta).

Theorem plus_assoc (alpha beta gamma : Ord) :
  alpha + (beta + gamma) = (alpha + beta) + gamma.

@@

Lemma finite_plus_ge_omega (n : nat) (alpha : Ord) :
  omega <= alpha -> n + alpha = alpha.
\end{Coqsrc}

@@

\begin{Coqsrc}
Fixpoint mult_Sn (alpha:Ord)(n:nat){struct n} :Ord :=
 match n with 
            | 0 => alpha
            | S p => mult_Sn alpha p + alpha
 end.

@@

\begin{Coqsrc}
Definition AP : Ensemble Ord :=
  fun alpha => 
  zero < alpha /\
  (forall beta, beta < alpha ->  beta + alpha = alpha).
\end{Coqsrc}

@@

\begin{Coqsrc}
Fixpoint omega_tower (i : nat) : Ord :=
  match i with
    0 =>  1
  | S j => phi0 (omega_tower j)
  end.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma AP_plus_closed (alpha beta gamma : Ord): 
     In AP alpha -> beta < alpha -> gamma < alpha -> beta + gamma < alpha.

@@

\begin{Coqsrc} 
Definition Closed (B : Ensemble Ord) : Prop := 
  forall M, Included M B -> Inhabited _ M -> 
                 countable M -> In B (|_| M).
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma AP_phi0 (alpha : Ord) : In AP (phi0 alpha).

@@

Lemma phi0_mono (alpha beta : Ord) :
  alpha < beta ->  phi0 alpha < phi0 beta.

Lemma phi0_inj (alpha beta : Ord) :
    phi0 alpha = phi0 beta -> alpha = beta.

Lemma phi0_sup : forall (U: Ensemble Ord),
   Inhabited _ U ->   countable U ->  phi0 (|_| U) = |_| (image U phi0).

Lemma is_limit_phi0 (alpha : Ord) :
  zero < alpha ->  is_limit (phi0 alpha).

@@

Lemma phi0_le (alpha : Ord) : alpha <= phi0 alpha.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma lt_phi0 (alpha : Ord):
  alpha < epsilon0 -> alpha < phi0 alpha.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition Cr_fun : forall alpha : Ord,
       (forall beta : Ord, beta < alpha -> Ensemble Ord) ->
        Ensemble Ord 
:= 
   fun (alpha :Ord)
        (Cr : forall beta, 
                beta < alpha -> Ensemble Ord) 
        (x : Ord) => (
       (alpha = zero /\ AP x) \/
       (zero < alpha /\
        forall beta (H:beta < alpha),
          the_ordering_segment (Cr beta H) x /\ ord (Cr  beta H) x = x)).

Definition Cr (alpha : Ord) : Ensemble Ord := 
    (Fix  all_ord_acc (fun (_:Ord) => Ensemble Ord) Cr_fun) alpha.
\end{Coqsrc}

\begin{Coqsrc}
Definition phi (alpha : Ord) : Ord -> Ord 
    :=  ord (Cr alpha).

Definition A (alpha : Ord) : Ensemble Ord :=
  the_ordering_segment (Cr alpha).
\end{Coqsrc}

@@

\begin{Coqsrc}
Section Proof_of_Lemma5.
  Let P (alpha:Ord) := Unbounded (Cr alpha) /\ Closed (Cr alpha).

@@

\begin{Coqsrc}
 Definition cnf_t := list Ord.

Fixpoint eval (l : cnf_t) : Ord :=
  match l with nil => zero
              | beta :: l' => phi0 beta + eval l'
  end.

@@

Definition is_cnf_of (alpha : Ord)(l : cnf_t) : Prop :=
  sorted l /\ alpha = eval l.
\end{Coqsrc}

@@

\begin{Coqsrc}
Theorem cnf_exists (alpha : Ord) :
  exists l: cnf_t, is_cnf_of alpha l.
\end{Coqsrc}

@@

Theorem cnf_exists_unique (alpha:Ord) :
  exists! l: cnf_t, is_cnf_of alpha l.
\end{Coqsrc}

@@

\section{An embedding of \texttt{T1} into \texttt{Ord}}

Our library 
\href{../src/html/hydras.Schutte.Injection_from_T1.html}%
{\texttt{Schutte.Injection\_from\_T1.v}} establishes the link between two very different modelizations of ordinal numbers. In other words, it ``validates'' a data structure in terms of
a classical mathematical discourse considered as a model. 
First, we define a function from \texttt{T1} into  \texttt{Ord} by structural recursion.

\begin{Coqsrc}
Fixpoint inject (t:T1) : Ord :=
 match t with 
     | T1.zero => zero
     | T1.ocons a n b =>  AP.phi0 (inject a) * S n + inject b
 end.  
\end{Coqsrc}

@@

Finally, we prove that \texttt{inject} is a bijection from the set of all terms of \texttt{T1} in normal form to the set 
\texttt{members epsilon0} of the elements of \texttt{Ord} strictly less than  $\epsilon_0$.
